Type Refinements for the Working Class

### 2015-12-22 paper.tex
more wording

In practice, the shift to a predicative topos with a large power object was a
mere technical nuisance, as all the constructions we needed to perform carried
over perfectly to this setting. For the remainder of this paper, we assume the
semantic universe $\Define{\SemU}{\Classes^\SCtx}$, the category of
copresheaves on symbol contexts. Every judgment $\mathcal{J}$ which we define
in this paper should be understood as such a presheaf, which is at each stage
$\Upsilon$ the class of derivations of $\mathcal{J}$ using symbols in
$\Upsilon$; we will also make use of \emph{internal} forms of judgment, which
are sections of $\Pow{X}$ for some object $X$.

>>>>

In practice, the shift to a predicative topos with a large power object was a
mere technical nuisance, as all the constructions we needed to perform carried
over perfectly to this setting. For the remainder of this paper, we assume the
semantic universe $\Define{\SemU}{\Classes^\SCtx}$, the category of
copresheaves on symbol contexts. Every judgment $\mathcal{J}$ which we define
in this paper should be understood as such a copresheaf, which is at each stage
$\Upsilon$ the class of derivations of $\mathcal{J}$ using symbols in
$\Upsilon$; we will also make use of \emph{internal} forms of judgment, which
are sections of $\Pow{X}$ for some object $X$.

Our purpose in fixing a semantic universe is emphatically \emph{not} to give an
interpretation or model of type theory inside set theory, though it is possible
to read our construction in this metamathematical light---however, the
vocabulary of the pretopos $\SemU$ gives us a perspicuous notation in which to
propound what we consider to be an informal (pre-mathematical) meaning
explanation in the sense of Heyting~\cite{heyting:1956} and
Martin-L\"of~\cite{martin-lof:1979}.
\footnote{
  Both Gambino~\cite{gambino:2002} and Dybjer~\cite{dybjer:2012} give lucid
  explanations of the distinction between \emph{meaning theory} and \emph{model theory}.
}
